Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
introduction: s/methodologies/methods/
introduction: language review: Haskell programmers, however ...

Haskell programmers, however, is apt to rely on the type system too
much and tend not to write test code.  For example, the Haskell
Platform 2011.4.0.0 contains 23 packages (not counting the 19 core
libraries that come with GHC), but only 8 of them have a test suite (5
provide example code, 10 have no tests nor examples).
A lack of tests is not only a quality and maintainability issue.  It
is also a lack of documentation.  Tests document how code is supposed
to be used; and tests documents the behavior of code.

>>>>

Haskell programmers, however, are apt to rely on the type system too
much and tend not to write test code.  For example, Haskell
Platform 2011.4.0.0 contains 23 packages, not counting the 19 core
libraries that come with GHC.  Only 8 of them have a test suite, 5
provide example code, and 10 have neither tests nor examples.
A lack of tests is not only a quality and maintainability issue.  It
also is a lack of documentation.  Tests document how code is supposed
to be used, and tests document the behavior of code.
